Storing messages with multipartite neural cliques

### 2014-07-17 Articles/article.tex
....

	\section{Introduction}

@@

	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}

@@

	$\tilde{W} = \max_{1\le i \le m} x_i x_i^\intercal$

	$W_{kl} = \bigg \{
  \begin{tabular}{ccc}
  $0$ & if $\exists i\in [1, c ], \, (i-1)c+1 \le k,l \le ic$ \\
  $\tilde{W}_{kl}$ & otherwise 
  \end{tabular}
  $

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$ as well).
		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}[!htb]
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to $S$}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

>>>>

	\begin{IEEEkeywords}
	associative memory, error correcting code, cliques, multipartite cliques, neural networks
	\end{IEEEkeywords}
	\section{Introduction}

@@

	Each message $x = (x_j)_{1 \le j \le c}$ is mapped to $y = (y_j)_{1 \le j \le c}$ where $y_j$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}

@@

	Units $k$ in cluster $j$ will be designated by index $l = (j-1)c+k$.

	The state of the network corresponds to a message.

	$\tilde{W} = \max_{1\le i \le m} x^i x^{i\intercal}$

	$W_{ll'} = \bigg \{
  \begin{tabular}{ccc}
  $0$ & if $\exists j\in [1, c], \, (j-1)c+1 \le l,l' \le jc$ \\
  $\tilde{W}_{ll'}$ & otherwise 
  \end{tabular}
  $

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$ as well).
		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :

		$x$

		$\tilde{x}$

		$s^{t} = \gamma \tilde{x^{t}} + W \tilde{x^{t}}$

		\begin{algorithm}[!htb]
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to $S$}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}
